Influence of Connectivity on Dung Beetle Communities

### 2025-03-03 corridor_docs/eric_ms_thesis/thesis_planning.Rmd
outlined discussion

1. dont forget o discuss the basic biology...why might a species be so common? why might one be rare?

>>>>

Recap main goals into findings
 abundances in matrix vs connected patch and why this could be happening
 - source pop to habiitat edge

 species richness again supporting that matrix is more of an ideal habitat for dung beetle community

 diversity indices community structures weren't highly different between patch types

 bray curtis hinting at similar land uses between corridor and winged patch
 - like julians paper corridors benefit certain populations and more fit populations are able to make better use

Interpretation of results
 Abundance 
 - reasin for highest abundances in matrix and connected patch
 - lower abundance in rectangle hinting at fragmentation effects
 Species Richness & Diversity
 - the role of hbitat connectivity in shaping community structure or lack thereof
 - why do we think connnected had lowest species richness??
 Functional traits and ecological impacts
 - did corridoors favor a functional trait
 - why might there be a trait response 
 - implications for ecosystem processes
 - like duung removal papers seed dispersal and yep

Comparing to previous studies
- how are things aligning
- think about the biology

Limitations and future work
- potential confounding factors (seasonality, distance from edge, sampling methodology and temmporal variation)
- other directions to go (dispersal -> radar, secifically measuring changes in ecosystem services)

Takeaways for conservation and management
- dung beetles are robust
- what do think about corridor design and considerations for fragmented lanndscapes
- practical applications think about the beetles
